---
title: "HS650_term_paper(4)"
author: "Xinchun Li"
date: "4/18/2018"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rvest)
#Load the data from website
site <- "http://wiki.socr.umich.edu/index.php/SOCR_Data_AD_BiomedBigMetadata"
wiki_url <- read_html(site)
html_nodes(wiki_url, "#content")
ad_data <- html_table(html_nodes(wiki_url,"table")[[1]])
head(ad_data)

ad_data[ad_data == "."] <- 0
ad_data$SymptomeChronicity <- as.numeric(ad_data$SymptomeChronicity)
ad_data$FAQTOTAL <- as.numeric(ad_data$FAQTOTAL)
ad_data$DX_Confidence <- as.numeric(ad_data$DX_Confidence)
ad_data$SymptomeSeverety <- as.numeric(ad_data$SymptomeSeverety)
ad_data$CTWHITE <- as.numeric(ad_data$CTWHITE)
ad_data$CTRED <- as.numeric(ad_data$CTRED)
ad_data$PROTEIN <- as.numeric(ad_data$PROTEIN)
ad_data$GLUCOSE <- as.numeric(ad_data$GLUCOSE)
ad_data$DX_Conversion <- as.numeric(ad_data$DX_Conversion)
ad_data$adascog <- as.numeric(ad_data$adascog)
ad_data$FAQTOTAL <- as.numeric(ad_data$FAQTOTAL)

ad_data <- ad_data[,-1]

lm1 <- lm(Weight_Kg~SymptomeSeverety, data = ad_data)
lm2 <- lm(Gender~SymptomeSeverety, data = ad_data)

cor(ad_data[c("adascog", "DXCURREN", "Weight_Kg","GLUCOSE", "CDHOME")])
car::vif(lm(DXCURREN ~ adascog + Weight_Kg + GLUCOSE + CDHOME, data=ad_data))
pairs(ad_data[c("adascog", "DXCURREN", "Weight_Kg","GLUCOSE", "CDHOME")])

library(psych)
pairs.panels(ad_data[, c("adascog", "DXCURREN", "Weight_Kg","GLUCOSE", "CDHOME")])

fit <- lm(SymptomeSeverety ~., data = ad_data)
fit
summary(fit)
plot(fit, which = 1:2)
step(fit,direction = "backward")
step(fit,direction = "forward")
step(fit,direction = "both")
step(fit,k=2)
step(fit,k=log(nrow(ad_data)))
fit2 = step(fit,k=2,direction = "backward")
summary(fit2)
plot(fit2, which = 1:2)
# Half-normal plot for leverages
# install.packages("faraway")
library(faraway)
halfnorm(lm.influence(fit)$hat, nlab = 2, ylab="Leverages")

# Train Data
set.seed(1234)
train_index <- sample(seq_len(nrow(ad_data)), size = 0.75*nrow(ad_data))
ad_train<-ad_data[train_index, ]
ad_test<-ad_data[-train_index, ]
#install.packages("rpart")
library(rpart)
ad.rpart<-rpart(DXCURREN ~ adascog + Weight_Kg + GLUCOSE + CDHOME, data=ad_train)
ad.rpart

# install.packages("rpart.plot")
library(rpart.plot)
rpart.plot(ad.rpart, digits=3)
rpart.plot(ad.rpart, digits = 4, fallen.leaves = T, type=3, extra=101)
# library(rattle)
# fancyRpartPlot(ad.rpart, cex = 0.8)
# ad.p<-predict(ad.rpart, ad_test)
# summary(ad.p)
# summary(ad_test$DXCURRE)
# cor(ad.p, ad_test$DXCURRE)
# MAE<-function(obs, pred){
  # mean(abs(obs-pred))
# 44}
# MAE(ad_test$DXCURRE, ad.p)
# mean(ad_test$DXCURRE)
# MAE(ad_test$DXCURRE, mean(ad_test$DXCURRE))xx
